# HsdMSR KO

We analyze the 6mA sites 0104 in this notebook

First, we need to have all the datas

## Load Data of MU
```{R}
# SMRT_MU from PacBio
SMRT_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/1448AMU_SMRT.gff", header = F,skip = 6)
SMRT_MU <- SMRT_MU[,c(1,5,7,6)]
colnames(SMRT_MU) <- c("Chromosome","Position","Strand","OriginalValue")
SMRT_MU <- get.chromosome.name(SMRT_MU)
SMRT_MU <- inner_join(SMRT_MU, Asites, by = c("Position", "Chromosome", "Strand"))
SMRT_MU <- arrange(SMRT_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
# Tombo direct 
Tombo_denovo_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/tombo_denovo.bed", sep="\t", header = T)
Tombo_denovo_MU <- Tombo_denovo_MU[,c(1,3,6,7)]
colnames(Tombo_denovo_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_denovo_MU <- arrange(Tombo_denovo_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
#Tombo_denovo_MU$Value <- round(Tombo_denovo_MU$OriginalValue,6)
# Tombo level_compare
Tombo_levelcom_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/tombo_levelcom.bed", sep="\t", header = T)
Tombo_levelcom_MU <- Tombo_levelcom_MU[, c(1,3,6,7)] # this OriginalValue is -log(p-OriginalValue)
colnames(Tombo_levelcom_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_levelcom_MU <- arrange(Tombo_levelcom_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
#Tombo_levelcom_MU$OriginalValue <- round(Tombo_levelcom_MU$OriginalValue,1)
# Tombo model_compare to WGA
Tombo_modelcom_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/tombo_modelcom.bed", sep="\t", header = T)
Tombo_modelcom_MU <- Tombo_modelcom_MU[, c(1,3,6,7)]
colnames(Tombo_modelcom_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_modelcom_MU <- arrange(Tombo_modelcom_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
# Tombo_modelcom_MU$OriginalValue <- round(Tombo_modelcom_MU$OriginalValue,3)
# mCaller_MU 
mCaller_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/mcaller.bed", sep="\t", header = F)
mCaller_MU <- mCaller_MU[,c(1,3,6,5)]
colnames(mCaller_MU) <- c("Chromosome","Position","Strand","OriginalValue")
mCaller_MU <- arrange(mCaller_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized() %>%
  get.chromosome.name2()
# Nanodisco_MU
Nanodisco_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/Nanodisco.csv", header = T)
Nanodisco_MU <- drop_na(Nanodisco_MU)
Nanodisco_MU$Strand <- ifelse(Nanodisco_MU$dir == "fwd", "+", "-")
Nanodisco_MU <- Nanodisco_MU[,c(1,2,10,8)] # The OriginalValue is t-test p-OriginalValue
colnames(Nanodisco_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Nanodisco_MU$OriginalValue <- -log10(Nanodisco_MU$OriginalValue)
Nanodisco_MU <- arrange(Nanodisco_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
# Dorado_MU+Modkit
Dorado_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/dorado.bed", header = F)
Dorado_MU <- Dorado_MU[,c(1,3,6,11)]
colnames(Dorado_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Dorado_MU <- arrange(Dorado_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
# hmmaerhead
Hammerhead_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/hammerhead.txt", sep="\t", header = TRUE)
Hammerhead_MU <- rbind(data.frame(Strand = "+", as.data.frame(Hammerhead_MU)),
                    data.frame(Strand = "-", as.data.frame(Hammerhead_MU)))
Hammerhead_MU <- Hammerhead_MU[,c(2,3,1,4)]
colnames(Hammerhead_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Hammerhead_MU <- arrange(Hammerhead_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
```

###Plot distribution of Value
```{R}
data.1448AMU <- rbind(data.frame(Category = 'ASMRT', as.data.frame(SMRT_MU)),
                      data.frame(Category = 'Tombo_denovo', as.data.frame(Tombo_denovo_MU)),
                      data.frame(Category = 'Tombo_levelcom', as.data.frame(Tombo_levelcom_MU)),
                      data.frame(Category = 'Tombo_modelcom', as.data.frame(Tombo_modelcom_MU)),
                      data.frame(Category = 'mCaller', as.data.frame(mCaller_MU)),
                      data.frame(Category = 'Nanodisco', as.data.frame(Nanodisco_MU)),
                      data.frame(Category = 'Dorado', as.data.frame(Dorado_MU)),
                      data.frame(Category = 'Hammerhead', as.data.frame(Hammerhead_MU))) %>%
  drop_na()

p2 <- ggplot(data.1448AMU, aes(x=Value, y=Category, fill=Category)) +
  geom_density_ridges(color = NA) +
  theme_ridges() + 
   scale_fill_manual(values = 
                      c("#B395BD","#98B85D","#7262AC","#AC667E","#287c9e","#BDA96F","#a9a9a9","#e29578"))+
  theme_bw() +
  ylab("Density") +
  xlab("Assigned Fraction Probability") +
  ggtitle("1448A ΔHsdMSR Assigned Fraction Distribution") +
  theme(legend.position = "none")

# ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/distribution/1448AMU.pdf", width = 8, height = 6, font="Arial")

rm(data.1448AMU)
```


### distribution of value in motifs

```{R}
dataset.name <- c("SMRT", "Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead")

MotifT2$OriginalValue <- 1
MotifT2$Rank <- 1
MotifT2$Value <- 1
type2 <- MotifT2
type2$index <- paste0(type2$Position, type2$Chromosome, type2$Strand)

type2_value_allT <- data.frame()

for ( i in dataset.name){
  print(i)
  temp <- get(paste0(i,"_MU"))
  temp$index <- paste0(temp$Position, temp$Chromosome, temp$Strand)
  a <- merge(type2,temp,by="index",all.x=T)
  a$Rank.y[is.na(a$Rank.y)] <- 1.223e7
  a$Value.y[is.na(a$Value.y)] <- 0
  # threshold <- sort(a$Rank.y, decreasing = F)[5]
  # a$label <- ifelse(a$Rank.y <= threshold, a$index,"")
  type2_value_allT <- rbind(type2_value_allT,data.frame(index = a$index,
                                                        name = i,
                                                        rank = a$Rank.y,
                                                        value = a$Value.y))
}


library(gghalves)
library(reshape2) 
library(ggrepel)

type2_value_allT$name <- gsub("AAASMRT","ASMRT",type2_value_allT$name)
type2_value_allT$name <- as.factor(type2_value_allT$name)
levels(type2_value_allT$name)
p1 <- ggplot(type2_value_allT[type2_value_allT$name != "Nanodisco" & type2_value_allT$name != "Hammerhead",], aes(x=name, y=log10(rank), fill=name)) + 
  # geom_point(position = position_jitter(width =0.05),size = 0.3, alpha = 0.3, color="lightgrey")+
  geom_half_violin(side='R', trim = T, color = NA) +
  theme_light() +
  coord_flip() +
  scale_fill_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578")) +
  xlab("") +
  ylab("") +
  ggtitle("Rank of true 6mA") +
  theme(panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        plot.title = element_text(size=12,hjust=0.5)) +
  scale_x_discrete(limits = rev(c("ASMRT","Dorado","mCaller","Tombo_denovo","Tombo_levelcom","Tombo_modelcom"))) 


p2 <- ggplot(type2_value_allT[type2_value_allT$name != "Nanodisco" & type2_value_allT$name != "Hammerhead",], aes(x=name, y=value, fill=name)) + 
  # geom_point(position = position_jitter(width =0.05),size = 0.3, alpha = 0.3, color="lightgrey") +
  geom_half_violin(side='R', trim = T, color = NA) +
  theme_light() +
  coord_flip() +
  scale_fill_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578")) +
  xlab("") +
  ylab("") +
  ggtitle("Value of true 6mA") +
  theme(panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        axis.text.y = element_blank(),
        plot.title = element_text(size=12,hjust=0.5),
        axis.ticks.y = element_blank())+
  scale_x_discrete(limits = rev(c("ASMRT","Dorado","mCaller","Tombo_denovo","Tombo_levelcom","Tombo_modelcom")))

p <- p1+p2
ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim_WT&MU/1448AMU_violin.pdf",p, width = 8.5, height = 3)


```


Then, we call the motifs.
## MEME_motifs
```{r}
library(memes)
library(seqinr)
library(GenomicRanges)
library(rtracklayer)
library(magrittr)
library(universalmotif)
library(Biostrings)
library(BSgenome)
library(ggplot2)
library(tidyr)
library(gridExtra)
# load fastq file and make it into stringset, ready for get_sequence
fasta_file <- "/Users/lubeifang/Desktop/BIOTOOLS/ref/1448A_formeme.fasta"
psph_stringset <- readDNAStringSet(fasta_file)

# define how to meme search
# We can change the batch search size for fasta and meme search way
get.meme <- function(sorted){
    sorted <- sorted[sorted$Position >= 20, ]
    bed <- data.frame(chr=sorted$Chromosome,
                      start=sorted$Position-1,
                      end=sorted$Position,
                      Starnd=sorted$Strand)
    gR <- GRanges(seqnames = bed$chr,
                  ranges = IRanges(start = bed$start, end = bed$end),
                  strand = "*")
    # resize ranges
    gRr <- resize(gR,40, "center") 
    sequences <- get_sequence(gRr, psph_stringset)
    # unique(width(gRr))
    # s <- data.frame(sequences)
  meme_results <- runStreme(sequences,control = "shuffle", minw = 8, maxw=10, nmotifs = 6)
  return(meme_results)
}


# Do the MEME
# set how many sites we would like to include
top = 10000
plot_list <- list()
meme_results.df <- data.frame()
top10k.df <- data.frame()
dataset.name <- c("SMRT", "Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead")
#dataset.name <- c("Dorado","Hammerhead")
for (i in dataset.name){
  print(i) 
#  i = "Hammerhead"
  file <- get(paste0(i,"_MU"))
  if (i == "mCaller" | i == "Dorado"){
    sorted1 <- file[order(file$Value, decreasing = T),][1:top,] # bigger to smaller
  }
  else{
    sorted1 <- inner_join(file, Asites, by = c("Chromosome","Position","Strand"))
    # Order it by Value, and get first top sites file
    sorted1 <- file[order(file$Value, decreasing = T),][1:top,] # bigger to smaller
  }
  sorted1 <- drop_na(sorted1) # SMRT for 0104LOSS have only 2873 rows
  
  # did this after peaks annotation, this only considered chromosome one.
#  temp <- data.frame(name = i, data.frame(inner_join(motif.peak.df, sorted1[sorted1$Chromosome=="chromosome"],
#                                                        by = c("Position"))))
  top10k.df <- rbind(top10k.df, data.frame(name = i, data.frame(sorted1)))
  
  meme_results <- get.meme(sorted1)
  meme_results.df <- rbind(meme_results.df, as.data.frame(Tool = i, data.frame(meme_results)))
  plot <- meme_results %>%
    to_list() %>%
    view_motifs()
  name=paste0(i,"_",top,"motif")
  plot <- plot + ggtitle(name)
  plot_list[[length(plot_list) + 1]] <- plot
}

# plot <- meme_results.df %>% 
#   to_list() %>% 
#   view_motifs()

g <- arrangeGrob(grobs = plot_list, nrow=2) 
ggsave(file="1448AMU_10000_6motifs.pdf", path = "/Users/lubeifang/Desktop/Benchmark/Figure/F2/",g, width = 32, height = 18)

# to_list(meme_results.df)
motif_detail <- meme_results.df[,c(-1,-17)]
write.csv(motif_detail,"/Users/lubeifang/Desktop/Benchmark/Figure/F2/1448AMU_10k_6motifs_memeresults.csv")
rm(get.meme)


count_data <- aggregate(Position ~ name + Chromosome + Strand, data = top10k.df, FUN = length)
p1<-ggplot(count_data, aes(x=name, y=Position, fill=Strand)) + 
  geom_bar(position="stack", stat = "identity") +
  scale_fill_manual(values = c("#E7BCC6","#FDCF9E"))+
  theme_bw()+
  ylab("Counts") +
  xlab("") +
  ggtitle("Strand distribution") +
  coord_flip() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))


p2 <-ggplot(count_data, aes(x=name, y=Position, fill=Chromosome)) + 
  geom_bar(position="stack", stat = "identity") +
  scale_fill_manual(values = c("#8A8DBF","#E7BCC6","#FDCF9E"))+
  theme_bw()+
  ylab("Counts") +
  xlab("") +
  ggtitle("Chromosome distribution") +
  coord_flip() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))

p <- p1+p2
ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F2/1448AMU_top10kdistri_strand&chr.pdf",p, width = 10, height = 6)

```

### top 10k peaks
```{R}
library(ChIPseeker)
library(ChIPpeakAnno)
library(clusterProfiler)
require(GenomicFeatures)
library(GenomicRanges)

# load annotation
ps_txdb <- makeTxDbFromGFF("/Users/lubeifang/Desktop/BIOTOOLS/ref/CHIPPEAKANNO/1448A_peak.gff")
annoData <- toGRanges(ps_txdb, feature="gene")

# Only consider Chromosome here
top10k.peak = data.frame()
dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead","SMRT")
for (i in dataset.name){
  print(i)
  peak <- top10k.df[top10k.df$Chromosome == "chromosome" & top10k.df$name == i,]
  peak_gr <- GRanges(seqnames="chr1",
                   ranges=IRanges(start=as.numeric(as.matrix(peak[,3]-1)),
                                  end= as.numeric(as.matrix(peak[,3])),
                                  names=as.matrix(as.matrix(peak[,1]))))
  annotatedpeak <- annotatePeakInBatch(peak_gr, AnnotationData=annoData)
  top10k.peak = rbind(top10k.peak, data.frame(Tool = i, as.data.frame(annotatedpeak)))
}


colnames(top10k.peak)
temp <- top10k.peak[,c(1,13)]
temp$Tool <- gsub("SMRT","ASMRT",temp$Tool)

# count how many sites of each tools got
count_data <- aggregate(distancetoFeature ~ Tool, data = temp, FUN = length)

ggplot(temp, aes(x=distancetoFeature, group=Tool, fill=Tool)) +
  geom_histogram(alpha = 0.6, binwidth = 30, color = "#CFCFE5") +
#  geom_density(alpha = 0.6, color = NA) +
  theme_bw() +
  facet_wrap(~Tool, nrow = 2) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5),
    # axis.text.x = element_text(family="Arial", size = 6),
    # axis.text.y = element_text(family="Arial", size = 12),
    # axis.title.x = element_text(family="Arial", size = 12),
    # axis.title.y = element_text(family="Arial", size = 12),
    strip.background = element_rect(colour="black", fill="#C6AEBA")) +
#  scale_fill_manual(values = c("#98B85D","#AC667E")) +
  xlab("Distance to Start Codon") +
  ylab("Count") +
  ggtitle("Distribution of 6mA location") +
  geom_text(data = count_data, aes(label = paste("Sites number : ",distancetoFeature), x = Inf, y = Inf), hjust = 1.05, vjust = 1.5, size = 3, color = "black") +
  xlim(-1000,2000)

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F2/1448AMU_top10kdistri_start.pdf", width = 10, height = 5)
```

### motif enrich sites and pvalue
```{R}
tool_detail <- data.frame(name=rep(c("ASMRT", "Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead"),1),
                          type=c(rep(c("Type 2 Motif"),8)),
                          nsites=as.numeric(c("327","1650","857","578","0","0","206","244")),
                          pval=as.numeric(c("2.4e-4","3e-26","9e-17","6.6e-10","0","0","7.2e-5","6.7e-6")))

# tool_detail<-subset(tool_detail, name!="SMRT")
tool_detail$pval <- round(-log(tool_detail$pval,10),2)
tool_detail[tool_detail=="Inf"] <- "0"
tool_detail$pval <- as.numeric(tool_detail$pval)
tool_detail <- tool_detail[order(tool_detail$name),]
tool_detail$name <- factor(tool_detail$name, levels = rev(tool_detail$name))

p3 <- ggplot() +
  geom_line(data = tool_detail, aes(x = name, y = nsites, group = type), color = "grey") +
  geom_point(data = tool_detail, aes(x = name, y = nsites), color = "#AC667E", size = 2) +
  theme_bw() +
  coord_flip()+
  ggtitle("number of sites") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab("") +
  ylab("")

# ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F2_table2motif/1448AMU_moitf_nsite.pdf", width = 7, height = 5, font="Arial")

p4 <- ggplot() +
  geom_line(data = tool_detail, aes(x = name, y = pval, group = type), color = "grey") +
  geom_point(data = tool_detail, aes(x = name, y = pval), color = "#AC667E", size = 2) +
  theme_bw() +
  coord_flip()+
  ggtitle("-log10(p-value)") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab("") +
  ylab("")

# p <- p1|p2|p3|p4
# ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F2/Moitf_detail.pdf", width = 12, height = 4)

```

We will focus on the sites then
Get trimed.df and draw F1 score
### trimed.df calculated
```{r}
dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado", "Hammerhead","SMRT")
# dataset.name <- c("SMRT")
trimed.df <- data.frame()

for (name in dataset.name){
  print(name)
  df <- get(paste0(name,"_MU"))
  # single mode
  if (name == "Dorado" | name == "mCaller"| name == "SMRT"){
      # Tombo_denovo and Hammerhead, they are ATCG and single mode, shift and 1.2e7 cutoffs
    trimed_temp <-  get.trim.df.A(df, MotifT2)
    trimed.df <- rbind(trimed.df, data.frame(Tool = name, as.data.frame(trimed_temp)))
  }
  else{
    trimed_temp <-  get.trim.df.ATCG(df, MotifT2)
    trimed.df <- rbind(trimed.df, data.frame(Tool = name, as.data.frame(trimed_temp)))
  }
  rm(trimed_temp)
  trimed.df[is.na(trimed.df)] <- 0
}
  

write.csv(trimed.df,"/Users/lubeifang/Desktop/Benchmark/intermediateFILE/1448AMU.trimed.df1114.csv")

```

## plot figures

### F1 score

```{R}
library(gridExtra)
library(patchwork)
trimed.df<-read.csv("/Users/lubeifang/Desktop/Benchmark/intermediateFILE/1448AMU.trimed.df1114.csv")
p <- ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=Rank, y=F1score, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_light() +
  xlab("Rank") +
  ylab("F1 score") +
  theme(
    panel.border = element_rect(color = "black", fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    panel.background = element_rect(fill='transparent'),
    legend.position="none"
  ) +
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))


pp <- ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=Rank, y=F1score, group=Tool, color=Tool))+
  geom_line(size=0.3) +
  theme_bw(base_size = 9) +
  theme(legend.position="none")+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578")) +
    xlim(0,10000)+
  xlab("")+
  ylab("")
p1 <- p + inset_element(pp, left = 0.3, bottom = 0.3, right = 0.95, top = 0.95) 
p1
# ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU1.pdf", p1, width = 3.3, height = 3)

p2<-ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=Recall, y=Precision, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_light() +
  theme(
    panel.border = element_rect(color = "black", fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    legend.position=c(0.3,0.3),
    legend.title = element_blank(),
    legend.text = element_text(size = 8),
    legend.key.height = unit(0.5, "mm"),
    legend.background = element_rect(fill = 'transparent', size = 0.3),
    panel.background = element_rect(fill='transparent')
  ) +
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))
# ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU2.pdf", p2, width = 3.3, height = 3)

p3<-ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=FPR, y=TPR, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_light() +
    theme(
    panel.border = element_rect(color = "black", fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    legend.position=c(0.55,0.18),
    legend.title = element_blank(),
    legend.text = element_text(size = 8),
    legend.key.height = unit(0.5, "mm"),
    legend.background = element_rect(fill = 'transparent', size = 0.3),
    panel.background = element_rect(fill='transparent')
  )+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))
#ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU3.pdf", p3, width = 3.3, height = 3)
```


### AUC
```{R}
# Calculate auc
get.auc <- function(tool,a,b) {
  a.vector <- trimed.df[trimed.df$Tool == tool,][[a]]
  a.vector <- c(0, a.vector, 1)
  b.vector <- trimed.df[trimed.df$Tool == tool,][[b]]
  b.vector <- c(0, b.vector, 1)
  area <- integrate(function(x) approx(a.vector, 
                                       b.vector, xout = x)$y, 
                    0, 1,subdivisions = 1000)
  return(area)
}



dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado", "Hammerhead","SMRT")
AUC <- data.frame()
for (k in c("trimed.df")){
  trimed.df<-get(k)
  for (i in dataset.name){
    area_PR <- get.auc(i, "Recall", "Precision")
    area_ROC <- get.auc(i, "FPR", "TPR")
    AUC <- rbind(AUC, data.frame(set=k,name = i, PRC = round(area_PR[["value"]],3), ROC = round(area_ROC[["value"]],3)))
  }
}

bar <- merge(AUC,best.df[best.df$Type == "BestF1",c(2,13)],by.x="name",by.y="Tool")
temp <-melt(bar,name="name")
p4<-ggplot(temp, aes(name, variable, fill=value)) + 
  geom_tile(alpha = 0.7) +
  geom_text(aes(label = round(value, 3)), color = "black", size = 3.5) + 
  theme_bw() +
  scale_fill_distiller(palette = "GnBu", trans = "reverse") +
  xlab("") +
  ylab("") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45,vjust=1,hjust=1),
        panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
# ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim_WT&MU/value_MU.pdf", width = 5, height = 4)
```


### small change
```{R}
a1 <- ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=log10(Rank), y=Precision, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_classic() +
  xlab("log10(Rank)") +
  ylab("Precision") +
  theme(
    axis.line = element_line(linewidth = 0.3),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill='transparent'),
    legend.position="none"
  ) +
  #xlim(0,10000)+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))
a2 <- ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=log10(Rank), y=Recall, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_classic() +
  xlab("log10(Rank)") +
  ylab("Recall") +
  theme(
    axis.line = element_line(linewidth = 0.3),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill='transparent'),
    legend.position="none"
  ) +
  #xlim(0,10000)+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))

#plota <- a1/a2
#ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU_P&R.pdf", plota, width = 2.7, height = 3.7)


b1 <- ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=log10(Rank), y=TPR, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_classic() +
  xlab("log10(Rank)") +
  ylab("TPR") +
  theme(
    axis.line = element_line(linewidth = 0.3),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill='transparent'),
    legend.position="none"
  ) +
 #xlim(0,10000)+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))
b2 <- ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=log10(Rank), y=FPR, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_classic() +
  xlab("log10(Rank)") +
  ylab("FPR") +
  theme(
    axis.line = element_line(linewidth = 0.3),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill='transparent'),
    legend.position="none"
  ) +
  #xlim(0,10000)+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))

#plotb <- b1/b2
#ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU_TPR&FPR.pdf", plotb, width = 2.7, height = 3.7)
p <- (p2 | (a1/a2) | p3 | (b1/b2)) + plot_layout(widths = c(2, 1.3, 2,1.3))
p
ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim_WT&MU/h.pdf", p, width = 11, height = 3)


# specificity
ggplot(trimed.df[trimed.df$Tool != "Nanodisco" & trimed.df$Tool != "Hammerhead",], aes(x=log10(Rank), y=TNR, group=Tool, color=Tool))+
  geom_line(size=0.4) +
  theme_classic() +
  xlab("log10(Rank)") +
  ylab("Specificity (FPR)") +
  theme(
    axis.line = element_line(linewidth = 0.3),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill='transparent'),
    legend.position="right"
  ) +
  #xlim(0,10000)+
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim_WT&MU/1448AMU_TNR.pdf", width = 5, height = 3)
```

### Get the best F1 score
```{R}
dataset.name <- c("SMRT","Tombo_levelcom", "Tombo_modelcom",  "Tombo_denovo", "mCaller", "Dorado")
best.df <- data.frame()

# Give a dataframe of best F1 with cutoff
for (k in dataset.name){
  # Get the row of best F1 score
  df.cate <- subset(trimed.df, Tool == k)
  df.cate <- subset(df.cate,F1score == max(df.cate$F1score))
  best.df.temp <- df.cate[order(df.cate$OriginalValue, decreasing = F),][1,]
  best.df.temp <- cbind(Type = "BestF1", best.df.temp)
  best.df <- rbind(best.df, best.df.temp)
  # Get the row of best Recall score
  df.cate <- subset(trimed.df, Tool == k) 
  df.cate <- subset(df.cate,Recall == max(df.cate$Recall))
  best.df.temp <- df.cate[order(df.cate$Recall, decreasing = F),][1,]
  best.df.temp <- cbind(Type = "BestRecall", best.df.temp)
  best.df <- rbind(best.df, best.df.temp)
  # Get the row of best Precision score
  df.cate <- subset(trimed.df, Tool == k) 
  df.cate <- subset(df.cate,Precision == max(df.cate$Precision))
  best.df.temp <- df.cate[order(df.cate$Precision, decreasing = F),][1,]
  best.df.temp <- cbind(Type = "BestPrecision", best.df.temp)
  best.df <- rbind(best.df, best.df.temp)
}
rm(best.df.temp, df.cate)

# write.csv(best.df,"/Users/lubeifang/Desktop/Benchmark/intermediateFILE/1448AMU.best.df1015.csv")
```

##Outliers
```{R}
library(ggVennDiagram)
library(ggrepel)
dataset.name <- c("SMRT", "Dorado",  "mCaller", "Tombo_denovo", "Tombo_levelcom", "Tombo_modelcom")
plot_list <- list()
outlier.df <- data.frame()

for (i in dataset.name){
  print(i)
  bestf1_V <- best.df[best.df$Tool == i & best.df$Type == "BestF1",]$Value
  
  df <- get(paste0(i,"_MU"))
  df_WGA <- get(paste0(i,"_WGA"))
  
  MU_temp <- subset(df, Value >= bestf1_V)
  MU_temp <- inner_join(MU_temp, Asites, by = c("Position", "Chromosome", "Strand"))
  WGA_temp <- subset(df_WGA, Value >= bestf1_V)
  WGA_temp <- inner_join(WGA_temp, Asites, by = c("Position", "Chromosome", "Strand"))

  outliers <- nrow(WGA_temp)
  temp <- inner_join(MU_temp, WGA_temp, by = c("Position", "Chromosome", "Strand"))
  temp_true <- inner_join(WGA_temp, MotifT2, by = c("Position", "Chromosome", "Strand"))
  
  x <- list(MU = paste0(MU_temp$Chromosome,MU_temp$Position,MU_temp$Strand),
          WGA = paste0(WGA_temp$Chromosome,WGA_temp$Position,WGA_temp$Strand),
          TrueMotif = paste0(MotifT2$Chromosome,MotifT2$Position,MotifT2$Strand))
  p <- ggVennDiagram(x, label_alpha = 0, edge_size = 0.3, label = "count") +
    scale_fill_gradient(low="white",high = "#C6AEBA") +
    theme(legend.position = "none")
  p <- p + ggtitle(i)
  plot_list[[length(plot_list) + 1]] <- p
  
  outlier.df <- rbind(outlier.df, data.frame(Tool = i, MU = nrow(MU_temp), WGA = nrow(WGA_temp), inter = nrow(temp),
                                             FCR = nrow(temp)/nrow(WGA_temp), ODR = nrow(WGA_temp)/nrow(MU_temp),
                                             OiGT = nrow(temp_true)))
}

g <- arrangeGrob(grobs = plot_list, nrow=2) 
ggsave(file="outliers_MU1030.pdf", path = "/Users/lubeifang/Desktop/Benchmark/Figure/F4_outlier/",g, width = 8, height = 6)



ggplot(outlier.df, aes(x=log(WGA,10), y=FCR, size = OiGT, color = Tool)) +
  geom_point(alpha=2) +
  theme_light() +
  xlab("log10(Outliers numbers)") +
  ylab("False Call Rate") +
  theme(legend.position = "bottom") +
  geom_text_repel(aes(label = Tool), size = 4, vjust = 0) + 
  scale_color_manual(values = c("#98B85D","#AC667E","#B395BD","#287c9e","#a9a9a9","#e29578"))

ggsave(file="bubbleMU1030.pdf", path = "/Users/lubeifang/Desktop/Benchmark/Figure/F4_outlier/", width = 4.8, height = 5.2)
```